Cycle Route Uptake and Scenario Estimation (CRUSE): an open and nationally scalable approach for strategic cycle network planning tool development \\\large{A case study of Ireland}

### 2024-03-23 paper.qmd
Add table caption ++

Tools for estimating geographical distribution of cycling potential have advanced substantially in recent years.
Developed by researchers and developers in academic, public and private sectors, they have evolved from simple area-based static models tailored to specific regions to more complex and (in some cases) more generalizable tools.
Outputs include maps with results available at several levels of analysis with levels of availability ranging from being only available to researchers and in static maps to open access mapping systems available to the public.
Some of the most relevant existing tools are summarised below and presented in Table 1.

@@

```{r}
knitr::kable(tools, caption = "Summary of existing tools for estimating cycling potential.", booktabs = TRUE) |>
  kableExtra::kable_styling(latex_options = "striped", full_width = FALSE) |>
  kableExtra::column_spec(1, width = "13em") |>
  kableExtra::column_spec(2, width = "15em") |>
  kableExtra::column_spec(3, width = "12em") |>
  kableExtra::column_spec(4, width = "5em")
```

>>>>

Tools for estimating geographical distribution of cycling potential have advanced substantially in recent years.
Developed by researchers and developers in academic, public and private sectors, they have evolved from simple area-based static models tailored to specific regions to more complex and (in some cases) more generalizable tools.
Outputs include maps with results available at several levels of analysis with levels of availability ranging from being only available to researchers and in static maps to open access mapping systems available to the public.
Some of the most relevant existing tools are summarised below and presented in @tbl-tools.

@@

```{r}
#| label: tbl-tools
knitr::kable(tools, caption = "Summary of existing tools for estimating cycling potential.", booktabs = TRUE) |>
  kableExtra::kable_styling(latex_options = "striped", full_width = FALSE) |>
  kableExtra::column_spec(1, width = "13em") |>
  kableExtra::column_spec(2, width = "15em") |>
  kableExtra::column_spec(3, width = "12em") |>
  kableExtra::column_spec(4, width = "5em")
```

### 2024-03-23 paper.tex
Add table caption ++

Tools for estimating geographical distribution of cycling potential have
advanced substantially in recent years. Developed by researchers and
developers in academic, public and private sectors, they have evolved
from simple area-based static models tailored to specific regions to
more complex and (in some cases) more generalizable tools. Outputs
include maps with results available at several levels of analysis with
levels of availability ranging from being only available to researchers
and in static maps to open access mapping systems available to the
public. Some of the most relevant existing tools are summarised below
and presented in Table 1.

\begin{longtable}[t]{>{\raggedright\arraybackslash}p{13em}>{\raggedright\arraybackslash}p{15em}>{\raggedright\arraybackslash}p{12em}>{\raggedright\arraybackslash}p{5em}}
\caption{\label{tab:unnamed-chunk-4}Summary of existing tools for estimating cycling potential.}\\
\toprule
Approach & Coverage and input data & Outputs and availability & License\\
\midrule
\cellcolor{gray!10}{Bicycle share model, Parkin et al. (2007)} & \cellcolor{gray!10}{England and Wales, Journeys to work OD census data, at the small-area (wards) level} & \cellcolor{gray!10}{Static tables in academic paper} & \cellcolor{gray!10}{Proprietary}\\
Analysis of  Cycling Potential (ACP), Transport for London (2010, 2016) & London, London Travel Demand Survey & Static tables, graphs, and heatmaps, not publicly available & Proprietary\\
\cellcolor{gray!10}{Prioritization index, Larsen et al. (2013)} & \cellcolor{gray!10}{Montreal, Survey, Road safety, and OD data} & \cellcolor{gray!10}{Map-based heatmap, not publicly available} & \cellcolor{gray!10}{Proprietary}\\
Usage intensity index, Zhang et al. (2014) & Belo Horizonte, Survey, census, and OD data & Static tables and maps, not publicly available & Proprietary\\
\cellcolor{gray!10}{The Cycling Potential Tool (CPT), Phillips and Range (2017)} & \cellcolor{gray!10}{Scotland, Environmental and socioeconomic data, at the small area (output areas) level} & \cellcolor{gray!10}{Maps showing cycling potential in each area} & \cellcolor{gray!10}{Proprietary}\\
\addlinespace
Propensity to Cycle Tool (PCT), Lovelace et al. (2017) & England and Wales, Journeys to work and school OD census data, at the small area (LSOA) level & Online maps, graphs, tables, publicly available at www.pct.bike & Open source\\
\cellcolor{gray!10}{The    Gross Potential for Cycling tool (CPC), Silva et al. (2021 and 2022)} & \cellcolor{gray!10}{21 Portuguese cities, Land use and socio-demographic data, at the small area (census tract) level} & \cellcolor{gray!10}{Static maps showing cycling potential in different areas} & \cellcolor{gray!10}{NA}\\
\bottomrule
\end{longtable}

>>>>

Tools for estimating geographical distribution of cycling potential have
advanced substantially in recent years. Developed by researchers and
developers in academic, public and private sectors, they have evolved
from simple area-based static models tailored to specific regions to
more complex and (in some cases) more generalizable tools. Outputs
include maps with results available at several levels of analysis with
levels of availability ranging from being only available to researchers
and in static maps to open access mapping systems available to the
public. Some of the most relevant existing tools are summarised below
and presented in Table~\ref{tbl-tools}.

\begin{longtable}[t]{>{\raggedright\arraybackslash}p{13em}>{\raggedright\arraybackslash}p{15em}>{\raggedright\arraybackslash}p{12em}>{\raggedright\arraybackslash}p{5em}}

\caption{\label{tbl-tools}Summary of existing tools for estimating
cycling potential.}

\tabularnewline

\\
\toprule
Approach & Coverage and input data & Outputs and availability & License\\
\midrule
\cellcolor{gray!10}{Bicycle share model, Parkin et al. (2007)} & \cellcolor{gray!10}{England and Wales, Journeys to work OD census data, at the small-area (wards) level} & \cellcolor{gray!10}{Static tables in academic paper} & \cellcolor{gray!10}{Proprietary}\\
Analysis of  Cycling Potential (ACP), Transport for London (2010, 2016) & London, London Travel Demand Survey & Static tables, graphs, and heatmaps, not publicly available & Proprietary\\
\cellcolor{gray!10}{Prioritization index, Larsen et al. (2013)} & \cellcolor{gray!10}{Montreal, Survey, Road safety, and OD data} & \cellcolor{gray!10}{Map-based heatmap, not publicly available} & \cellcolor{gray!10}{Proprietary}\\
Usage intensity index, Zhang et al. (2014) & Belo Horizonte, Survey, census, and OD data & Static tables and maps, not publicly available & Proprietary\\
\cellcolor{gray!10}{The Cycling Potential Tool (CPT), Phillips and Range (2017)} & \cellcolor{gray!10}{Scotland, Environmental and socioeconomic data, at the small area (output areas) level} & \cellcolor{gray!10}{Maps showing cycling potential in each area} & \cellcolor{gray!10}{Proprietary}\\
\addlinespace
Propensity to Cycle Tool (PCT), Lovelace et al. (2017) & England and Wales, Journeys to work and school OD census data, at the small area (LSOA) level & Online maps, graphs, tables, publicly available at www.pct.bike & Open source\\
\cellcolor{gray!10}{The    Gross Potential for Cycling tool (CPC), Silva et al. (2021 and 2022)} & \cellcolor{gray!10}{21 Portuguese cities, Land use and socio-demographic data, at the small area (census tract) level} & \cellcolor{gray!10}{Static maps showing cycling potential in different areas} & \cellcolor{gray!10}{NA}\\
\bottomrule

\end{longtable}
